Spatial Reasoning and Statistical Graphics

### 2014-10-17 Paper/Draft1/TestingVisualAptitude.Rnw
fix incorrect reference key.

The advantage of using tests from the Kit of Factor Referenced Cognitive tests \citep{ekstrom1976manual} is that the tests are extremely well studied \citep{voyer1995manual}
\comment{the bib file is not updated on the repo}
and comparison data are available from the validation of these factors. The card rotation, paper folding, and figure classification tests have been validated using different populations, many of which are demographically similar to Iowa State students (naval recruits, college students, late high-school students, and 9th grade students).

>>>>

The advantage of using tests from the Kit of Factor Referenced Cognitive tests \citep{ekstrom1976manual} is that the tests are extremely well studied \citep{voyer1995magnitude} and comparison data are available from the validation of these factors. The card rotation, paper folding, and figure classification tests have been validated using different populations, many of which are demographically similar to Iowa State students (naval recruits, college students, late high-school students, and 9th grade students).
